% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% !Mode:: "TeX:UTF-8"

\documentclass{resume}
\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\usepackage{linespacing_fix} % disable extra space before next section
\usepackage{cite}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Shawn Xiaoheng Hong}

% {E-mail}{mobilephone}{homepage}
% be careful of _ in emaill address
\contactInfo{Mobile / +61 426857350}{Email: shawn.hong@outlook.com}{}{} 
% {E-mail}{mobilephone}
% keep the last empty braces!
%\contactInfo{xxx@yuanbin.me}{(+86) 131-221-87xxx}{}


% 
% \section{Work Rights \& Skills}
% \begin{itemize}
%   \item Permanent Resident of NSW with full working rights in Australia (190 visa)
%   \item C++ / C / Python / JS / React / Flask / Shell / MongoDB / MySQL
% \end{itemize}

% intel Devops
% \section{Core Skills}
% \begin{itemize}
%   \item Excellent English Skills: TOFEL-106/120, PTE-90/90, GRE-323, Australian Permanent Resident 
%   \item Solid programming experience in Python, C++, JS, Bash and Perl. 
%   \item Relevant Knowledge in BIOS, web techs, data science etc. Experience with web frameworks as Flask \& React.
% \end{itemize}


% % talenza gp 澳洲
% \section{Basic Info}
% \begin{itemize}
%   \item Permanent Resident of NSW with full working rights in Australia (190 visa).
%   \item Solid programming experience in C++, Python, JS, Bash and Perl. 
% \end{itemize}

% % 小红薯 后端
% \section{Basic Info}
% \begin{itemize}
%   \item Solid programming skills in C/C++, Python, JavaScript, Bash and Perl.
%   \item Sound experience in both frontend and backend with familiarity in relevant frameworks.  
% \end{itemize}

% % 携程 前端
% \section{Basic Info}
% \begin{itemize}
%   \item Hands on experience on React.JS and AJAX. Knowledge in frontend/backend separation structure.
%   \item Familiarity in relevant frameworks, TCP/IP stacks, data structures and datbase.  
% \end{itemize}

% % 苏州微软
% \section{Basic Info}
% \begin{itemize}
%     \item Permanent Resident of NSW with full working rights in Australia (190 visa).
%     \item Solid programming experience in C++, Python, JS and Bash. Understanding of algorithms and data structures.
%     \item Perception in end-user experience with knowledge on both frontend \& backend developments. 
% \end{itemize}

% % Billigence
% \section{Basic Info}
% \begin{itemize}
%     \item Solid programming experience in C++, Python, JS and Bash. Understanding of algorithms and data structures.
%     \item Perception in end-user experience with knowledge on both frontend \& backend developments. 
%     \item Excellent English Skills: Australian Permanent Resident, TOFEL-106/120, PTE-90/90, GRE-323,  
% \end{itemize}

% % NextGen.Net
% \section{Basic Info}
% \begin{itemize}
%     \item Solid programming experience in C++, Python, JS and Bash. Understanding of algorithms and data structures.
%     \item Hands-on experince of React based frontend developments \& RESTful backend developments. 
%     \item Permanent Resident of NSW with full working rights in Australia (190 visa).
% \end{itemize}
% % Dear Hiring Manager,
% % I am Hong Xiaoheng graduating from UNSW's Master of Information Technology by September this year. My main coding languages are C++, Python and JS with extensive practices in algorithms using C++. I have solid experience of both frontend and RESTful backend development using React.JS, Flask, Redis, MongoDB, MySQL etc. 
% % I am an Australian Permanent Resident and therefore do not require further help with visa. The attached is my detailed resume. Please kindly consider my application to the graduate software engineer role in your company. 
% % Best Regards,
% % Hong Xiaoheng

% % ANS 
% \section{Basic Info}
% \begin{itemize}
%   \item Permanent Resident of NSW with full working rights in Australia (190 visa).
%   \item Proficiency in Python, C/C++, OOP designing and Bash scripting. Knowledge of Java from university courses.
%   \item Familiarty with frontend, backend and SQL/NoSQL datbase. Ability \& passion to learn new technologies.
% \end{itemize}

% % Hello fresh
% \section{Basic Info}
% \begin{itemize}
%     \item Solid programming experience in C++, Python, JS, HTML/CSS and Bash. 
%     Hands-on experince of frontend developments \& RESTful backend developments using
%     Flask, Redis, MongoDB and Postgres. 
%     \item Permanent Resident of NSW with full working rights in Australia (190 visa).
% \end{itemize}
% % Dear Hiring Manager

% % 网易
% \section{Basic Info}
% \begin{itemize}
%     \item Solid programming experience in C++, Python, JS and Bash. Understanding of algorithms and data structures.
%     \item Perception in end-user experience with knowledge on both frontend \& backend developments. 
% \end{itemize}

% thales
\section{Basic Info}
\begin{itemize}
    \item Solid programming experience in C++, Python, JS, HTML/CSS and Bash. 
    Hands-on experince of frontend developments \& RESTful backend developments using
    Flask, Redis, MongoDB and Postgres. 
    \item Permanent Resident of NSW with full working rights in Australia (190 visa).
\end{itemize}

% \section{Coding Skills}
% \begin{itemize}
  
% \end{itemize}

% \section{\faGraduationCap\ 教育背景}
\section{Education}
\datedsubsection{\textbf{University of New South Wales}\textit{}}{2019.07 - 2021.09}
\begin{itemize}
\item Master of Information Technology. Graduating with Distinction grades.
\end{itemize}

\datedsubsection{\textbf{University of Chinese Academy of Science}\textit{}}{2014.09 - 2017.06}
\begin{itemize}
\item  Master of Science in Physics. Outstanding Graduate Student Award of Shanghai.
\end{itemize}

\datedsubsection{\textbf{East China Normal University}\textit{}}{2010.09 - 2014.06}
\begin{itemize}
\item Bachelor of Science. Outstanding Graduate Student Award of Shanghai 
\end{itemize}

% \end{itemize}

\section{Work Experience}
\datedsubsection{\textbf{Zeyuan Capitcal}, Software Engineering Intern, Remote}{2020.06 - 2020.12}
\begin{itemize}
  \item Participated in implementing the trading strategies for industrial and iron ore futures in Python \& C++.
\end{itemize}

\datedsubsection{\textbf{Shanghai Automotive Industry Corporation}, Solid State Battery Scientist}{2017.07 - 2018.10}
\begin{itemize}
  \item Research of solid state electrolytes, cathode materials and structures for all solid state lithium batteries.
\end{itemize}


\section{Projects}

\datedsubsection{\textbf{Recipes sharing website - Backend}}{Flask, MongoDB, Redis}
\begin{itemize}
  \item A recipes sharing website built by a group of 5 people. I am in charge of the backend whilst the other 4 frontend.
  \item RESTful API based backend services built on top of Flask. Swagger UI is used for documentation and API testing. JSON Web Token is applied for authentication.
  \item Built a Redis caching layer to cache hot data. Adopted cache aside structure to ensure the eventual consistency where data is deleted from the cache after updated in the main DB. Improved API responsing time from 100-200ms to 20-50ms with the caching layer applied.
  \item MongoDB is used as the main DB. The full text search function is built based on the index and search pipeline.
  \item Obtained full mark as the final project of the degree. Future plan is to deploy the application to cloud service, develop online chat function and message queue service.
\end{itemize}

\datedsubsection{\textbf{Markowitz portfolio optimization program}}{Numpy, Pandas}
\begin{itemize}
  \item Developed and optimized a program for computing the maximized portfolio based on Markowitz model. Based on over 200 trading strategies, the history performance of each in a given period of term is analyzed to give the most optimal portfolio (minimized risk/maximized return/maximized Sharpe ratio).
  \item For multiple future commodities, the return/retracement ratio are largely improved from 2 - 3 to 4 -5 after applied with the computed optimized portfolio.
\end{itemize}


\datedsubsection{\textbf{Online Quiz website - Frontend}}{React}
\begin{itemize}
  \item An online quiz website. Functionalities for teachers' side include quiz creation \& edition, quiz progress control and history statistics summary. Students' side features include quiz participation and result summary.
  \item The single page application interact with backend APIs using AJAX request. 
\end{itemize}

\datedsubsection{\textbf{Wearable social distancing alerting program}}{C, Contiki}
\begin{itemize}
  \item Based on Contiki-OS, end device e.g. TI cc2650 communicate with each other via 802.15.4 in star topology local area network. Distances between two device are measured using received signal strength indicator. Close contact less than 2 meters is sent back to end server via TCP to record potential close contact.
\end{itemize}

\section{Publications, total citation 343}
%\begin{itemize}
  J. Power Sources 324 (2016); J. Mater. Chem. A 5 (2017); J. Mater. Chem. A 4.43
  (2016); J. Power Sources 342 (2017); J. Mater. Chem. A 5 (2017); ACS
  Appl. Mater. Inter. 9.34 (2017); Energy Storage Mater. 11 (2018)
%\end{itemize}

\end{document}
